PHQ-4-R: Adaptation of the 4-item screening for Anxiety and Depression for a subclinical sensitivity

### 2023-01-16 README.Rmd
update

- Murphy, J., Brewer, R., Plans, D., Khalsa, S. S., Catmur, C., & Bird, G. (2020). [Testing the independence of self-reported interoceptive accuracy and attention](https://journals.sagepub.com/doi/full/10.1177/1747021819879826). Quarterly Journal of Experimental Psychology, 73(1), 115-133. https://doi.org/10.31234/osf.io/fqgu4

**Aim**. Re-analyze the raw data from [Murphy et al. (2020)](https://journals.sagepub.com/doi/full/10.1177/1747021819879826) (study 1) regarding the factor structure of the Interoceptive Accuracy Scale (IAS) by using the *Method Agreement Procedure* for the number of factors to extract and performing a CFA model comparison.

**Conclusion**. EFA suggested a 1-factor and 4-factors solutions, but the latter was favoured by CFA. Additionally, CFA suggested that a 5-factors model (obtained by separating *Nociception* from *Interoception*) was superior:

- *Interoception*: Heart, Hungry, Breathing, Thirsty, Temperature, Sexual arousal.
- *Nociception*: Muscles, Bruise, Pain.
- *Expulsion*: Burp, Sneeze, Wind.
- *Elimination*: Vomit, Defecate, Urinate.
- *Skin*: Itch, Tickle, Affective touch.

The final revised scale, made of 18 items (6 for interoception and 3 per secondary dimension), is available below.

## Data

Data from the [study 1](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) was downloaded from OSF.

```{r, message=FALSE, warning=FALSE, results='asis'}
library(tidyverse)
library(easystats)

df <- haven::read_sav("Study 1.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Gender == 1, "Male", "Female")))

report::report_participants(df, age = "Age", sex = NA, gender = "Gender")
```

## EFA

```{r, message=FALSE, warning=FALSE}
data <- select(df, -Age, -Gender)

n <- parameters::n_factors(data)

n
plot(n)
```

The *Method Agreement Procedure*

```{r, message=FALSE, warning=FALSE}
efa1 <- parameters::factor_analysis(data, n=1, sort = TRUE)
efa1

efa4 <- parameters::factor_analysis(data, n=4, rotation = "oblimin", sort = TRUE)
efa4
```

## CFA

We compared the two models suggested by EFA (1-factor and 4-factors), with two additional model based on the latter: one with 2 items removed (Blood sugar and Taste), and one with additionally the *Interoception* factor split into two (with the pain-related items grouped together).

```{r, message=FALSE, warning=FALSE}
library(lavaan)

cfa1 <- lavaan::cfa(parameters::efa_to_cfa(efa1, 
                                           names="IAS"), data=data)
cfa4 <- lavaan::cfa(parameters::efa_to_cfa(efa4, 
                                           names=c("Skin", "Expulsion", "Interoception", "Elimination"),
                                           threshold = "max"), data=data)

cfa4mod <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Cough + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal + Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

cfa5 <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Cough + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
Nociception =~ Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

anova(cfa1, cfa4, cfa4mod, cfa5)
```

## Final Model

Additionally, we removed the least loaded items of expulsion (cough) to improve the balance (3 items per secondary scales, and 6 for interoception).

```{r, message=FALSE, warning=FALSE}
cfa5mod <- "
Skin =~ Affective_touch + Tickle + Itch
Expulsion =~ Sneeze + Wind + Burp
Interoception =~ Heart + Hungry + Breathing + Thirsty + Temp + Sex_arousal
Nociception =~ Muscles + Bruise + Pain
Elimination =~ Urinate + Defecate + Vomit
" |> 
lavaan::cfa(data=data)

anova(cfa5, cfa5mod)
```

```{r, message=FALSE, warning=FALSE}
parameters::parameters(cfa5) |> 
  display()
```

```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=10}
library(tidySEM)

graph_data <- tidySEM::prepare_graph(cfa5mod, 
                   layout=get_layout(cfa5mod, layout_algorithm = "layout_with_kk"), 
                   variance_diameter=NA)

nodes(graph_data) <- nodes(graph_data) |> 
  mutate(fill = ifelse(shape == "rect", "grey", "#F06292"))

plot(graph_data)
```

## Final Scale

>>>>

<sub>A reanalysis of Murphy, J., Brewer, R., Plans, D., Khalsa, S. S., Catmur, C., & Bird, G. (2020). [Testing the independence of self-reported interoceptive accuracy and attention](https://journals.sagepub.com/doi/full/10.1177/1747021819879826). Quarterly Journal of Experimental Psychology, 73(1), 115-133. https://doi.org/10.31234/osf.io/fqgu4</sub>

## IAS-R
